A Bayesian ranking statistic to find \\high-mass black holes in LIGO data

### 2021-01-28 main.tex
Updates from Overleaf

Tuning the prior odds can dramatically affect the \pastrobcr. For example, consider Table~\ref{tab:tuningresults}, which reports tuned \pastrobcr and un-tuned \untunedpastrobcr (where $\alpha=1$ and $\beta=1$) for various high-mass events and candidates. By tuning the prior odds, the \pastrobcr for some IAS events (for example, GW170403 and GW170817A) can change by more than 0.5, resulting in the promotion/demotion of a candidate's significance.
\input{Data/tuning_results_table}

>>>>

Tuning the prior odds can dramatically affect the \pastrobcr. For example, consider Table~\ref{tab:tuningresults}, which reports tuned \pastrobcr and un-tuned \untunedpastrobcr (where $\alpha=1$ and $\beta=1$) for various high-mass events and candidates. By tuning the prior odds, the \pastrobcr for some IAS events (for example, GW170403 and GW170817A) can change by more than 0.5, resulting in the candidate being promoted/demotion of candidate significance. 
\input{Data/tuning_results_table}
